---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# carsimr.rios

<!-- badges: start -->
[![R-CMD-check](https://github.com/zac-d-rios/carsimr.rios/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/zac-d-rios/carsimr.rios/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of carsimr.rios is to simulate car movements for various different car densities, while also allowing the user to visualize these movements.

## Installation

You could install the development version of carsimr.rios, if it were public, from [GitHub](https://github.com/zac-d-rios/carsimr.rios) with:

``` r
# install.packages("devtools")
devtools::install_github("zac-d-rios/carsimr.rios")
```

## Example

This is an example of how to initialize a grid, first with a proportion and then with an integer number of cars

```{r example1}
library(carsimr.rios)
example1 <- initialize_grid(0.5, c(5, 3), 0.7)

example2 <- initialize_grid(8, c(5, 3), 0.5)

example1
```

```{r example2}
example2
```

Notice how they both have the same number of cars, but with a different proportion of blue cars (represented by 2). Specifically, example1 has about 70% blue cars, while example2 has about 50%.

For moving the cars, use the move cars function, which takes a carsimr object and number of iterations to move.

```{r cars}
move_cars(example2, 2)
```

Notice how blue cars (2's) moved upwards during the first move, and red cars moved rightwards during the second move.


Shown below is an example of plotting the movements of cars through various iterations

```{r at_once,figures-side, fig.show="hold", out.width="33.33%"}
plot(move_cars(initialize_grid(rho = 0.3, c(5, 5), p = 0.5), trials = 5))
```
